A bad day of studying is better than a good day of sleeping

### 2020-12-26 paper/paper.tex
feat: non prio revision

\subsection{DP-AGM postulates}
The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here. $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$ and $\ast$ being a belief change operator on epistemic states.

@@

\begin{example}
    \label{example:example-updated-tpo}
    Reconsidering the tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}). When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it depending on if it is an $\alpha$-world or not. In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot. For this example $x_{1}, x_{2}$ and $x_{3}$ are $[\neg\alpha]$-worlds while $x_{4}$ is an $[\alpha]$-world.

@@

\subsection{Non priotised revision}
% show also: new evidence that does not become part of the belief set -> non prio example, explain what it is
\subsection{The problem of just moving things one up}

% TODO write chapter
\section{Properties of tpo-revision operators}
%    \item Properties of $\ast_{\preceq}$, their explanation

@@

\subsection{Example operator}
% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on. USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
%TODO this could be OWN contribution!!?

% TODO write chapter
\section{Sentinential view, do we even need this?}
%    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set. Show of properties for the family of revision operators using sentinential view. Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
%\end{itemize}
%\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it. Show of axiomatic definition of the family of operators in semantic and sentinential view. Establishing theorem 1.

\section{Summary}

>>>>

\subsection{DP-AGM postulates}
\label{chapter:dp-agm-postulates}
The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here. $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$ and $\ast$ being a belief change operator on epistemic states.

@@

\begin{example}
    \label{example:example-updated-tpo}
    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}). When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not. In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot. For this example $x_{1}, x_{2}$ and $x_{3}$ are $[\neg\alpha]$-worlds while $x_{4}$ is an $[\alpha]$-world.

@@

\subsection{Non-prioritised revision}

Belief revision with the AGM postulates \cite{Alchourron1985} or the reformulation by Darwiche and Pearl \cite{Darwiche1997} always includes the new information $\alpha$ in the belief set after revision. This feature is explicit in \ref{E2} of DP-AGM from chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}) given as $\alpha \in B(\mathbb{E}\ast\alpha)$.

The operators characterised by Booth and Meyer do not require new evidence $\alpha$ to be part of the revised belief set which makes them part of non-prioritised revision \cite{Hansson1999}.

An example is already given in example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}. The belief set extracted from the new epistemic state $\mathbb{E}$ as $[B(\mathbb{E})] = min(\top, \leq_{\alpha}^{\ast})$ includes the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$ and therefor does not include the new evidence $\alpha$.

%Although the approach described allows us to determine more than just
%the belief set associated with an epistemic state, there is a problem with this
%approach regarding iterated tpo-revision. While the extra structure tells us
%how to determine a new tpo, it tells us nothing about how to determine the
%new extra structure which is needed to guide the next revision. Clearly the
%problem of iterated belief revision has simply re-emerged “one level up”. We
%investigate this problem by considering some desirable properties for revising
%the extra structure, and prove the consistency of these properties by giving a
%concrete operator satisfying all of them.

% TODO write chapter
\section{Properties of Booth and Meyer tpo-revision operators}
%    \item Properties of $\ast_{\preceq}$, their explanation

@@

% TODO write chapter
\subsection{Sentinential view}
%    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set. Show of properties for the family of revision operators using sentinential view. Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
%\end{itemize}
%\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it. Show of axiomatic definition of the family of operators in semantic and sentinential view. Establishing theorem 1.

\section{Revising $\preceq$}
% DO NOT DO THIS? OR mention that we only show a concrete operator and not discuss properties, see discussion
\subsection{Example operator}
% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on. USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
%TODO this could be OWN contribution!!?

% TODO write chapter
\section{Discussion}
\subsection{Iterating on the iterator}
The revision operator $\ast$ based on $\preceq$ allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$. To be useful in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised, as Booth and Meyer put it the problem has "re-emerged 'one level up'" \cite{Booth2011}. In their paper Booth and Meyer discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$ denoted as $\$$, their properties and how to revise them. For more information on SPH revision see \cite{Booth2011}.
